Cell Decompositions for Rank Two Quiver Grassmannians

### 2017-12-22 Grassmannian_cells.tex
Reorganization and says

@@

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}\footnote{we should have $P_m=(\Sigma_iP_{m-1})^T$}
  \label{rem:reflection recursion}
  These representations satisfy the following recursions using the reflection functors:
  \[P_1=S_1,\quad P_m=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m=\Sigma_1 I_{m-1}\]
  for $m\ge2$.
  In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$. 
\end{remark}

@@

\begin{corollary}
  For $V\in Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable.
\end{corollary}
\begin{proof}
  Applying the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map from $\Hom(P_{m+1}^V,P_{m+1}^V)$ to the one-dimensional space $\Hom(P_{m+1},P_{m+1}^V)$.
  In particular, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
\end{proof}

\begin{corollary}
  \label{cor:preprojective homomorphism duality}
  The sequence \eqref{eq:AR sequence} gives rise to an isomorphism $H_m^*\cong H_{m-1}$.
\end{corollary}
\begin{proof}
  Define a map $H_m^*\to H_{m-1}$ by $\varphi\mapsto\bar{\varphi}:=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\bar{\varphi}$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
  Suppose $\varphi\in H_m^*$ is a nonzero functional on $H_m$ and let $V\subsetneq H_m$ denote the kernel of $\varphi$.
  Then $\bar{\varphi}=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
  But then Lemma~\ref{le:injective evaluation maps} implies $\iota_{m-1}$ is the zero map, a contradiction.
  Thus the map $H_m^*\to H_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.
\end{proof}
\begin{remark}
  The set $Gr(H_m)$ is naturally a poset and Corollary~\ref{cor:preprojective homomorphism duality} gives an identification of the opposite poset $Gr(H_m)^{op}\cong Gr(H_m^*)$ with $Gr(H_{m-1})$.
  We write $\bar{V}\subset H_{m-1}$ for the subspace corresponding to $V\subset H_m$ under this identification.
  Under the isomorphism of $H_{m-1}$ with $H_m^*$, we have $\bar{V}=(H_m/V)^*$.
\end{remark}
Following Remark~\ref{rem:reflection recursion}, the reflection functor $\Sigma_1$ provides a natural identification of $H_m$ with $H_{m-1}$ for $m\ge2$. 
Combining with Corollary~\ref{cor:preprojective homomorphism duality} we obtain a natural isomorphism $H_m^*\cong H_m$ for $m\ge2$.
The next observation is essential for the results to follow.
\begin{proposition}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\bar{\bar{V}}=\tau V$.
\end{proposition}
\begin{proof}
  We show that $\bar{\bar{\varphi}}=\tau\varphi$ for $\varphi\in H_m$.
  Indeed, we have
  \[\bar{\bar{\varphi}}=(id\overline{\otimes}\bar{\varphi})\circ\iota_{m-2}=\Big(id\overline{\otimes}\big((id\overline{\otimes}\varphi)\circ\iota_{m-1}\big)\Big)\circ\iota_{m-2}.\]
\end{proof}

The total Grassmannian $Gr(H_m)$ is naturally a poset under inclusion which we extend to a $\CC$-linear category $\CC Gr(H_m)$ with objects the elements of $Gr(H_m)$ and at most one morphism (up to scalars) between any two objects.
Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in Gr(H_m)$.
\begin{lemma}
  \label{le:unique morphisms}
  The functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC Gr(H_m)\cong\cP_{m+1}$.
  In particular, there exists a morphism $P_{m+1}^W\to P_{m+1}^V$ for $V,W\in Gr(H_m)$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
\end{lemma}
\begin{proof}
  Given $V,W\in Gr(H_m)$, we apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V).\]
  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional, spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$. 
\end{proof}

@@

@@

\begin{lemma}
  \label{le:unique truncated extension}
  For $V\in Gr(H_m)$, $m\ge2$, the space $\Ext(P_{m+1}^V,P_{m-1})$ is one-dimensional and spanned by the extension
  \begin{equation}
    \label{eq:unique extension}
    \xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.375){\kappa_V} & P_m\otimes(H_m/V) \ar[r] & P_{m+1}^V \ar[r] & 0}.
  \end{equation}
\end{lemma}
\begin{proof}
  Applying the functor $\Hom(-,P_{m-1})$ to the sequence \eqref{eq:truncated preprojectives} gives an isomorphism $\Ext(P_{m+1}^V,P_{m-1})\cong\Ext(P_{m+1},P_{m-1})$ with a one-dimensional space.
  Writing $X$ for the unique extension of $P_{m+1}^V$ by $P_{m-1}$, this isomorphism gives rise to the following pullback diagram:
  \[\xymatrix{ & & 0 \ar[d] & 0\ar[d] & \\
    & & P_m\otimes V \ar@{=}[r]\ar[d] & P_m\otimes V\ar[d] & \\
    0 \ar[r] & P_{m-1} \ar@{=}[d]\ar[r]^(.425){\iota_{m-1}} & P_m\otimes H_m \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1} \ar[r]\ar[d] & 0\\
    0 \ar[r] & P_{m-1} \ar[r]^{\kappa_V} & X \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
    & & 0 & 0 & }\]
  from which we immediately obtain the isomorphism $X\cong P_m\otimes(H_m/V)$.
\end{proof}
\begin{corollary}
  \label{cor:truncated preprojective isomorphism}
  Suppose $V\in Gr(H_m)$ has codimension one in $H_m$.  Then $P_{m+1}^V\cong P_m^{\bar{V}}$.
\end{corollary}
\begin{proof}
  By Lemma~\ref{le:unique truncated extension}, we have the exact sequence
  \[\xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.35){\kappa_V} & P_m\otimes(H_m/V) \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
  But $H_m/V$ is a one-dimensional vector space and so $P_m\otimes(H_m/V)\cong P_m$.
  Under this identification, the left hand morphism $\kappa_V$ in the sequence above identifies with a generator of $\bar{V}$ and thus $P_{m+1}^V\cong P_m^{\bar{V}}$.
\end{proof}
\begin{corollary}
  For $V,W\in Gr(H_m)$, $m\ge3$, the space $\Ext(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})$ has dimension 0 or 1.. .
\end{corollary}

\begin{lemma}
  \label{le:more truncated homomorphisms}
  For $W\in Gr(H_m)$, $m\ge2$, the following hold:
  \begin{enumerate}
    \item $\Hom(P_{m-1},P_m^{\bar{W}})\cong W^*$;
    \item $\Hom(P_{m+1},P_m^{\bar{W}})\cong (H_m/W)^*$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  By Corollary~\ref{cor:preprojective homomorphism duality}, we have $H_{m-1}\cong H_m^*$ and $\bar{W}\cong(H_m/W)^*$.
  Then Lemma~\ref{le:truncated homomorphisms} gives the isomorphism
  \[\Hom(P_{m-1},P_m^{\bar{W}})\cong H_{m-1}/\bar{W}\cong H_m^*/(H_m/W)^*\cong W^*.\]

  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:AR sequence} we get an exact sequence 
  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes H_m,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m-1},P_m^{\bar{W}}) \ar[r] & 0}.\]
  By Lemma~\ref{le:basic homological properties}, the middle space above is isomorphic to $H_m^*$ and thus $\Hom(P_{m+1},P_m^{\bar{W}})$ can be identified with the kernel of the natural map $H_m^*\to W^*$, i.e.\ with the space $(H_m/W)^*$.
\end{proof}
\begin{remark}
  For $W\in Gr(H_m)$, $m\ge2$, a nonzero element $\varphi\in\Hom(P_{m+1},P_m^{\bar{W}})=(H_m/W)^*$ corresponds, by taking the kernel of $\varphi$, to a codimension 1 subspace $V\subset H_m$ containing $W$.
  Then the map $\varphi$ is (up to scalars) the composition of the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, the isomorphism $P_{m+1}^V\cong P_m^{\bar{V}}$ from Corollary~\ref{cor:truncated preprojective isomorphism}, and the unique projection $P_m^{\bar{V}}\to P_m^{\bar{W}}$.
\end{remark}
\begin{corollary}
  For $V,W\in Gr(H_m)$, $m\ge2$, we have natural isomorphisms 
  \[\Hom(P_{m+1}^V,P_m^{\bar{W}})\cong\big(H_m/(V+W)\big)^*\quad\text{and}\quad\Ext(P_{m+1}^V,P_m^{\bar{W}})\cong(V\cap W)^*.\]
\end{corollary}
\begin{proof}
  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:truncated preprojectives} we get an exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes V,P_m^{\bar{W}}) \ar[r] & \Ext(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & 0}.\]
  By Lemma~\ref{le:more truncated homomorphisms}, we may identify $\Hom(P_{m+1}^V,P_m^{\bar{W}})$ and $\Ext(P_{m+1}^V,P_m^{\bar{W}})$ with the kernel and cokernel of the natural map $(H_m/W)^*\to V^*$.
  The result immediately follows from this.
\end{proof}
\begin{remark}
  It is slightly easier to understand the dual of the diagram figuring in the proof above, in particular it is immediate that the kernel of the natural morphism $V\to H_m/W$ is $V\cap W$ while the cokernel of this morphism is $H_m/(V+W)$.
\end{remark}

@@

For $V\in Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
\begin{lemma}
  For $V\in Gr(H_m)$, $m\ge1$, given any proper subrepresentation $X\subsetneq P_{m+1}^V$, the upper pullback sequence
  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  splits for every proper subspace $W\subsetneq V$.
\end{lemma}
\begin{proof}
  We proceed by induction on $\codim_V W$.  
  When $\codim_V W=1$, we have an exact sequence
  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\] 
  with both morphisms irreducible by Lemma~\ref{le:irreducible morphisms} and the claim immediately follows.

@@

@@

\begin{lemma}\label{le:properties}The following holds:
\begin{enumerate}
 \item For $m\geq 2$, we have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
   % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
   %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0;$$
		\item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
		\[\ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.\]
		On the universal covering, we have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\kk$  where $k\neq j_i$ for $i=1,\ldots,l$, $\Hom(\tilde P_m,\tilde P_m^{\uj})=\kk$, $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.

		\end{enumerate}
\end{lemma} 
\begin{proof}The first statement follows from Theorem \ref{covering}. For $m=1$, the second part is obvious. For $m\geq 2$, it then follows by applying the identities (\ref{recursive}).

@@

For every $i=1,\ldots,l$, we have $\Hom(\tilde P_{m-1,j_i},\bigoplus_{i=1}^l \tilde P_{m-1,j_i})\cong\Hom(\tilde P_{m-1,j_i},\tilde P_m)=\kk$. Thus it follows that $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\tilde P^{\uj}_{m})=0$ because the representations $\tilde P_{m-1,j_i}$ are exceptional. Thus we obtain the last identity when applying $\Hom(\underline{\quad},\tilde P^{\uj}_{m})$.

\end{proof} 
%To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.

>>>>

%\usepackage[marginal]{showlabels}

@@

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}
  \footnote{we should have $P_m=(\Sigma_iP_{m-1})^T$}
  \sayD{We need to change the conventions above to include notation for the equivalence between $\rep K(n)$ and $\rep K(n)^{op}$.}
  \label{rem:reflection recursion}
  These representations satisfy the following recursions using the reflection functors:
  \[P_1=S_1,\quad P_m=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m=\Sigma_1 I_{m-1}\]
  for $m\ge2$.
  In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$. 
\end{remark}

@@

\begin{lemma}
  \label{le:unique morphisms}
  There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ for $V,W\in Gr(H_m)$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
\end{lemma}
\begin{proof}
  Given $V,W\in Gr(H_m)$, we apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V).\]
  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional, spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$. 
\end{proof}

\begin{corollary}
  For $V\in Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable.
\end{corollary}
\begin{proof}
  By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
\end{proof}

\begin{remark}
  The total Grassmannian $Gr(H_m)$ is naturally a poset under inclusion which we extend to a $\CC$-linear category $\CC Gr(H_m)$ with objects the elements of $Gr(H_m)$ and at most one morphism (up to scalars) between any two objects.
  Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in Gr(H_m)$.
  By Lemma~\ref{le:unique morphisms}, the functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC Gr(H_m)\cong\cP_{m+1}$.
\end{remark}

@@

\begin{lemma}
  \label{le:unique truncated extension}
  For $V\in Gr(H_m)$, $m\ge2$, the space $\Ext(P_{m+1}^V,P_{m-1})$ is one-dimensional and spanned by the extension
  \begin{equation}
    \label{eq:unique extension}
    \xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.375){\kappa_V} & P_m\otimes(H_m/V) \ar[r]^(.625){ev} & P_{m+1}^V \ar[r] & 0}.
  \end{equation}
\end{lemma}
\begin{proof}
  Applying the functor $\Hom(-,P_{m-1})$ to the sequence \eqref{eq:truncated preprojectives} gives an isomorphism $\Ext(P_{m+1}^V,P_{m-1})\cong\Ext(P_{m+1},P_{m-1})$ with a one-dimensional space.
  Writing $X$ for the unique extension of $P_{m+1}^V$ by $P_{m-1}$, this isomorphism gives rise to the following pullback diagram:
  \[\xymatrix{ & & 0 \ar[d] & 0\ar[d] & \\
    & & P_m\otimes V \ar@{=}[r]\ar[d] & P_m\otimes V\ar[d] & \\
    0 \ar[r] & P_{m-1} \ar@{=}[d]\ar[r]^(.425){\iota_{m-1}} & P_m\otimes H_m \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1} \ar[r]\ar[d] & 0\\
    0 \ar[r] & P_{m-1} \ar[r]^{\kappa_V} & X \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
    & & 0 & 0 & }\]
  from which we immediately obtain the isomorphism $X\cong P_m\otimes(H_m/V)$.
\end{proof}

\begin{lemma}
  \label{le:preprojective homomorphism duality}
  The sequence \eqref{eq:AR sequence} gives rise to an isomorphism $H_m^*\cong H_{m-1}$.
\end{lemma}
\begin{proof}
  Define a map $H_m^*\to H_{m-1}$ by $\varphi\mapsto\bar{\varphi}:=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\bar{\varphi}$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
  Suppose $\varphi\in H_m^*$ is a nonzero functional on $H_m$ and let $V\subsetneq H_m$ denote the kernel of $\varphi$.
  Then $\bar{\varphi}=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
  But then Lemma~\ref{le:injective evaluation maps} implies $\iota_{m-1}$ is the zero map, a contradiction.
  Thus the map $H_m^*\to H_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.
\end{proof}
\begin{remark}
  The set $Gr(H_m)$ is naturally a poset and Lemma~\ref{le:preprojective homomorphism duality} gives an identification of the opposite poset $Gr(H_m)^{op}\cong Gr(H_m^*)$ with $Gr(H_{m-1})$.
  We write $\bar{V}\subset H_{m-1}$ for the subspace corresponding to $V\subset H_m$ under this identification.
  Under the isomorphism of $H_{m-1}$ with $H_m^*$, we have $\bar{V}=(H_m/V)^*$.
\end{remark}

\begin{corollary}
  \label{cor:truncated preprojective isomorphism}
  Suppose $V\in Gr(H_m)$ has codimension-one in $H_m$.  Then $P_{m+1}^V\cong P_m^{\bar{V}}$.
\end{corollary}
\begin{proof}
  By Lemma~\ref{le:unique truncated extension}, we have the exact sequence
  \[\xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.35){\kappa_V} & P_m\otimes(H_m/V) \ar[r]^(.625){ev} & P_{m+1}^V \ar[r] & 0}.\]
  But $H_m/V$ is a one-dimensional vector space and so $P_m\otimes(H_m/V)\cong P_m$.
  Under this identification, the left hand morphism $\kappa_V$ in the sequence above identifies with a generator of $\bar{V}$ and thus $P_{m+1}^V\cong P_m^{\bar{V}}$.
\end{proof}

Following Remark~\ref{rem:reflection recursion}, the reflection functor $\Sigma_1$ provides a natural identification of $H_m$ with $H_{m-1}$ for $m\ge2$. 
Combining with Lemma~\ref{le:preprojective homomorphism duality} we obtain a natural isomorphism $H_m^*\cong H_m$ for $m\ge2$.
The next observation is essential for the results to follow.
\begin{proposition}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\bar{\bar{V}}=\tau V$.
\end{proposition}
\begin{proof}
  \sayD{Proof needed}
  We show that $\bar{\bar{\varphi}}=\tau\varphi$ for $\varphi\in H_m$.
  Indeed, we have
  \[\bar{\bar{\varphi}}=(id\overline{\otimes}\bar{\varphi})\circ\iota_{m-2}=\Big(id\overline{\otimes}\big((id\overline{\otimes}\varphi)\circ\iota_{m-1}\big)\Big)\circ\iota_{m-2}.\]
\end{proof}

@@

\begin{corollary}
  For $V,W\in Gr(H_m)$, $m\ge3$, the space $\Ext(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})$ has dimension 0 or 1.. .
\end{corollary}

\begin{lemma}
  \label{le:more truncated homomorphisms}
  For $W\in Gr(H_m)$, $m\ge2$, the following hold:
  \begin{enumerate}
    \item $\Hom(P_{m-1},P_m^{\bar{W}})\cong W^*$;
    \item $\Hom(P_{m+1},P_m^{\bar{W}})\cong (H_m/W)^*$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  By Lemma~\ref{le:preprojective homomorphism duality}, we have $H_{m-1}\cong H_m^*$ and $\bar{W}\cong(H_m/W)^*$.
  Then Lemma~\ref{le:truncated homomorphisms} gives the isomorphism
  \[\Hom(P_{m-1},P_m^{\bar{W}})\cong H_{m-1}/\bar{W}\cong H_m^*/(H_m/W)^*\cong W^*.\]

  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:AR sequence} we get an exact sequence 
  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes H_m,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m-1},P_m^{\bar{W}}) \ar[r] & 0}.\]
  By Lemma~\ref{le:basic homological properties}, the middle space above is isomorphic to $H_m^*$ and thus $\Hom(P_{m+1},P_m^{\bar{W}})$ can be identified with the kernel of the natural map $H_m^*\to W^*$, i.e.\ with the space $(H_m/W)^*$.
\end{proof}
\begin{remark}
  For $W\in Gr(H_m)$, $m\ge2$, a nonzero element $\varphi\in\Hom(P_{m+1},P_m^{\bar{W}})=(H_m/W)^*$ corresponds, by taking the kernel of $\varphi$, to a codimension-one subspace $V\subset H_m$ containing $W$.
  Then the map $\varphi$ is (up to scalars) the composition of the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, the isomorphism $P_{m+1}^V\cong P_m^{\bar{V}}$ from Corollary~\ref{cor:truncated preprojective isomorphism}, and the unique projection $P_m^{\bar{V}}\to P_m^{\bar{W}}$.
\end{remark}
\begin{corollary}
  For $V,W\in Gr(H_m)$, $m\ge2$, we have natural isomorphisms 
  \[\Hom(P_{m+1}^V,P_m^{\bar{W}})\cong\big(H_m/(V+W)\big)^*\quad\text{and}\quad\Ext(P_{m+1}^V,P_m^{\bar{W}})\cong(V\cap W)^*.\]
\end{corollary}
\begin{proof}
  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:truncated preprojectives} we get an exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes V,P_m^{\bar{W}}) \ar[r] & \Ext(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & 0}.\]
  By Lemma~\ref{le:more truncated homomorphisms}, we may identify $\Hom(P_{m+1}^V,P_m^{\bar{W}})$ and $\Ext(P_{m+1}^V,P_m^{\bar{W}})$ with the kernel and cokernel of the natural map $(H_m/W)^*\to V^*$.
  The result immediately follows from this.
\end{proof}
\begin{remark}
  It is slightly easier to understand the dual of the diagram figuring in the proof above, in particular it is immediate that the kernel of the natural morphism $V\to H_m/W$ is $V\cap W$ while the cokernel of this morphism is $H_m/(V+W)$.
\end{remark}

@@

For $V\in Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
\sayD{The next results need some serious clean-up, can they be proven for $K(n)$ without passing to the universal cover?}
\begin{lemma}
  For $V\in Gr(H_m)$, $m\ge1$, given any proper subrepresentation $X\subsetneq P_{m+1}^V$, the upper pullback sequence
  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  splits for every proper subspace $W\subsetneq V$.
\end{lemma}
\begin{proof}
  We proceed by induction on $\codim_V W$.  
  When $\codim_V W=1$, we have an exact sequence
  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\] 
  with both morphisms irreducible by Lemma~\ref{le:irreducible morphisms} and the claim immediately follows.

@@

In this section, we fix compatible bases for each $H_m=\Hom(P_{m-1},P_m)$ and use these to lift the (truncated) preprojectives to the universal cover of $K(n)$.
This lifting will rigidify the situation and allow more precise control over these representations and their subrepresentation structure.

@@

\begin{lemma}
  \label{le:properties}
  \sayD{Parts (2) and (3) should follow directly from Lemma~\ref{le:unique morphisms} and the definition of truncated preprojectives for $K(n)$.} 
  The following holds:
  \begin{enumerate}
    \item For $m\geq 2$, we have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
    % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
    %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0;$$
    \item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
      \[\ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.\]
      On the universal covering, we have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\kk$  where $k\neq j_i$ for $i=1,\ldots,l$, $\Hom(\tilde P_m,\tilde P_m^{\uj})=\kk$, $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.
  \end{enumerate}
\end{lemma} 
\begin{proof}
  The first statement follows from Theorem \ref{covering}.
  For $m=1$, the second part is obvious.
  For $m\geq 2$, it then follows by applying the identities (\ref{recursive}).

@@

  For every $i=1,\ldots,l$, we have $\Hom(\tilde P_{m-1,j_i},\bigoplus_{i=1}^l \tilde P_{m-1,j_i})\cong\Hom(\tilde P_{m-1,j_i},\tilde P_m)=\kk$. Thus it follows that $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\tilde P^{\uj}_{m})=0$ because the representations $\tilde P_{m-1,j_i}$ are exceptional. Thus we obtain the last identity when applying $\Hom(\underline{\quad},\tilde P^{\uj}_{m})$.
\end{proof} 
%To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.
